### 2021-01-12 LaTeX-USENIX/sections/paper.tex
candidate for submission

While Solidity and EVM are like many common programming languages, they also have quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object oriented design, clearing mappings). We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it. The bottom line is that the current benchmark for a \cm-esque design is in the low hundreds of trade executions per block on Ethereum today. This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators. However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum}. While roll-ups use centralized servers and are thus no fully on-chain, we consider an architecture where these servers only interface with Ethereum and never interface directly with users, which side-steps the regulatory hook that is present in many other server-augmented trading platforms (including both decentralized exchanges like 0x and EtherDelta, and roll-ups like Loopring, all described below).

@@

The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}. TEX is also an implementation of an orderbook however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain orderbook is. It is similar to our variant with roll-ups however it uses a different architecture where users interact directly with the off-chain component (a regulatory hook). The other overlap is the focus on resisting front-running attacks. In a recent survey on front-running attacks in blockchain~\cite{eskandari2019sok}, three solutions are proposed. One solution is to provide confidentiality over the content of orders which is the approach taken by TEX. The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders. The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third party service~\cite{Kla20} (a regulatory hook). These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A. Juels. \href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}). The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach we take here.

@@

\cm is designed as base class that can be extended and customized. We discuss potential modifications here.

@@

The second solution is to levy a carefully computed fee against the traders for every new order they submit. These fees are accumulated by the DApp to use as a bounty. When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty. This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost. However an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading. If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.
%= = = = = =  = =  =  Rollups=  = = = = = = = = =%

\subsection{Off-chain Closing}
\label{sec:rollups}

\textblue{Re-align this section}

We have two main motivations for designing an \textit{on-chain} order book: (1) the trust model is superior to partially/fully centralized solutions, and (2) \cm can be deployed without any delay or other arrangements. We have relaxed (2) already by considering services like Ethereum Alarm Clock and any.sender to facilitate easy market closings. In this section, we present a variant that only provides (1) (however one that can be deployed without any other market stakeholders).

In our \cm variant with rollups, the token issuer does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). Recall that on-chain, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With roll-ups, 38 pairs cost 38,863 gas. As the pairs increase, the cost is essentially constant (\eg 1000 pairs cost 38,851 as opposed to 457,326,935 on-chain). Submitting an order costs 39,169 gas on average as opposed to 207,932 on-chain.

Our \cm variant is not the first rollup-based order book. Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book. The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant requires on-chain submission. While on-chain submission is hampered by Ethereum's block limits, the threat model of reordering transactions is well-understood and our call market design mitigates most front-running attacks. In Loopring 3.0, the rollup proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book. In short, we provide better protection against a malicious exchange while Loopring 3.0 provides even better performance.

@@

@@

It may seem paradoxical or unethical to build for regulators exactly what they worry about, however we agreed that it was too difficult to answer our research questions without actual implementation and experimentation. \cm is proof of concept code that implements only enough to understand the feasibilty of on-chain trading and we release the code for reproducibility. However it is not production code, it is unpolished, it has no UI, and we have no intention of promoting it for adoption. Finally, by understanding the `pain points' in the design, we found we were constantly tugged toward centralized components (Ethereum alarm clock, meta-transactions, roll-up servers, \etc) which could serve as regulatory hooks even if the service is mainly on-chain.

>>>>

While Solidity and EVM are like many common programming languages, they also have quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object oriented design, clearing mappings). We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it. The bottom line is that the current benchmark for a \cm-esque design is in the low hundreds of trade executions per block on Ethereum today. This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators. However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `rollups'~\cite{kalodner2018arbitrum}. While rollups use centralized servers and are thus no fully on-chain, we consider an architecture where these servers only interface with Ethereum and never interface directly with users, which side-steps the regulatory hook that is present in many other server-augmented trading platforms (including both decentralized exchanges like 0x and EtherDelta, and rollups like Loopring, all described below).

@@

The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}. TEX is also an implementation of an orderbook however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain orderbook is. It is similar to our variant with rollups however it uses a different architecture where users interact directly with the off-chain component (a regulatory hook). The other overlap is the focus on resisting front-running attacks. In a recent survey on front-running attacks in blockchain~\cite{eskandari2019sok}, three solutions are proposed. One solution is to provide confidentiality over the content of orders which is the approach taken by TEX. The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders. The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third party service~\cite{Kla20} (a regulatory hook). These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A. Juels. \href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}). The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach we take here.

@@

%\cm is designed as base class that can be extended and customized. We discuss potential modifications here.

@@

The second solution is to levy a carefully computed fee against the traders for every new order they submit. These fees are accumulated by the DApp to use as a bounty. When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty. This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost. However an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading. If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.

@@

%= = = = = =  = =  =  Rollups=  = = = = = = = = =%

\section{\cm Variant with Off-chain Closing}
\label{sec:rollups}

We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks. However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, rollup architectures like Loopring, and commit-chain solutions like TEX). We briefly consider an alternative design that is almost as difficult to regulate as a fully on-chain solution. In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders. Traders still only interact with Ethereum.

In our \cm variant with rollups, the token issuer does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). Recall that on-chain, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With rollups, 38 pairs cost 38,863 gas. As the pairs increase, the cost is essentially constant (\eg 1000 pairs cost 38,851 as opposed to 457,326,935 on-chain). Submitting an order costs 39,169 gas on average as opposed to 207,932 on-chain.

Our \cm variant is not the first rollup-based order book. Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book. The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant uses on-chain submission so that the rollup server does not need to be publicly reachable. Loopring 3.0 can operate near high frequency trading as order submission is unhampered by Ethereum, however its  rollup proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book. Traders who prioritize trade fairness might opt for a solution like our variant, while traders who want speed would vastly prefer the Loopring architecture which offers near-CEX speed while being non-custodial. Loopring leaves a regulatory hook whereas our variant could be nearly as difficult to regulate as a fully on-chain solution if the rollup server was kept anonymous: Ethereum and Arbitrum themselves would be the only regulatory hooks.

@@

It may seem paradoxical or unethical to build for regulators exactly what they worry about, however we agreed that it was too difficult to answer our research questions without actual implementation and experimentation. \cm is proof of concept code that implements only enough to understand the feasibilty of on-chain trading and we release the code for reproducibility. However it is not production code, it is unpolished, it has no UI, and we have no intention of promoting it for adoption. Finally, by understanding the `pain points' in the design, we found we were constantly tugged toward centralized components (Ethereum alarm clock, meta-transactions, rollup servers, \etc) which could serve as regulatory hooks even if the service is mainly on-chain.
